In-class Challenge 1
========================================================

Name: | StudentNumber:
------|------
Max Hollmann | 2180812

Assignment:
-----------

### 1
**Suppose you are going to play a lottery in which you need 6 (not necessarily unique) numbers, from 0-99. Create a vector containing your 6 numbers, and save the vector in a variable called lottery.**

```{r}
print(lottery <- sample(0:99, size = 6, replace = TRUE))
```

### 2
**Use the max() and min() function on your lottery variable. What do these functions return? Are the results scalars, vectors, or matrices?**

```{r}
min(lottery)
max(lottery)
```

Results are scalars, since there's only one highest and lowest value.

### 3
**Use the sample() function on your lottery variable. Based on the results, what do you think the sample() function does? Is the result a scalar, vector, or matrix?**

```{r}
sample(lottery)
```

It takes a random sample from the lottery vector, apparently using all elements without replacement by default.

### 4

**Consider the following code:** 
```{r, eval=FALSE}
max(sample(lottery))
```
 
**What would you expect this code to return?**

The same as the max call above, as the sample contains all elements of the lottery vector.

**Run the code by copying and pasting the code into R. Are your predictions met? Fix any problems the code might have. What does the code do now? Is this what you would have expected? Is the result a scalar, vector, or matrix?**

Yes. It's a scalar.

### 5
**Consider the code in exercise 4 above, except with the max and sample swapped. What would you expect this code to do? Are your predictions met? Is the result a scalar, vector, or matrix?**

It will return the same, since in this case it will find the highest value in `lottery` and then take a *random* sample from this vector of size 1.

### 6
**If you wanted to access just the first value of lottery and save it in a variable, how would you do this?**

```{r, eval=FALSE}
var <- lottery[1]
```

### 7
**Consider the following code:**
```{r}
print(lottery2 <- outer(lottery,lottery,'-'))
```

**Run the code, and save the result in a variable called lottery2. Based on the results, can you tell what the outer function did? Is the result a scalar, vector, or matrix?**

It takes combines each element of the vector with all elements through the specified function, in this case subtraction. The result is a matrix with `length(lottery)` rows and colums.

### 8
**If you wanted to just access the value in the second row, third column of lottery2 and save that single value in a variable, how would you do it? Check the value contained in your new variable. Is it correct?**

```{r}
print(var <- lottery2[2, 3])
```

Yay!

### 9
**If you wanted to save the whole second row as a new variable, how would you do it? Will this new variable contain a scalar, vector, or matrix?**

```{r}
print(row2 <- lottery2[2,])
```

Surprise! It's a vector.