In-class Challenge 7
========================================================

Name: | StudentNumber:
------|------
Max Hollmann | 2180812

Assignment:
-----------

### 1
**Create a function that plots a blank tic-tac-toe board, using the details discussed in the lecture. Call this function `createBoard()`.**
```{r}
createBoard <- function() {
  plot(NA, xlim=c(0, 3), ylim=c(3, 0), main='The Board', xlab='', ylab='', asp=1, axes=TRUE)
  # Add the vertical and horizontal lines.
  # Hint: take a look at ?abline
  
  # black out the illegal area
  rect(-9999, -9999, 9999, 9999, col = 'black')
  rect(0, 0, 3, 3, col = 'white')
  
  # draw grid
  abline(0, 0, h = 1:2, v = 1:2)
}
```


### 2
**Create a 3x3 matrix of all 0s called `board`. The matrix will be R's representation of the game board.**
```{r}
board <- matrix(0, 3, 3)
```


### 3
**Use the `locator()` function to click on the plot and get an input. How does the output of `locator()` match up with the rows and columns of the matrix? What do you have to do to the output of the locator function to turn it into a row and a column that matches your matrix?** 

It gives the exact point on the plot where the user clicked. Since we need integers as indices for the board matrix, we can simply round up these values to the next higher integer. Then we can use x as the column index, and y as the row index.


### 4
**Write a function called `getMove()` that converts the output of `locator()` into the corresponding row and column of the `board` matrix.**
```{r}
getMove <- function() {
  repeat {
    loc <- locator(1)
    
    # convert information in "loc" to the variables "row" and "column".
    # Hint: take a look at ?floor and ?ceiling and ?round - which is most helpful?
    row = ceiling(loc$y)
    column = ceiling(loc$x)
    if (row %in% 1:3 && column %in% 1:3) break # only exit the loop when row and column are valid
  }
  
  # then 
  return(c(row, column))
}
```



### 5
**Given your `board` matrix exists and has 1's and -1's in it, what's the best way to figure out whose turn it is? Write a function that returns 1 if it's Player 1's move and -1 if it's Player 2's move.**
```{r}
whoseTurnIsIt <- function(board) {
  # do something to figure out whose turn it is
  # Hint: find out what the modulus operator does and how it could be useful in this case.
  
  # this assumes that player 1 always begins. Thus, it's player 2's turn
  # if the number of moves done is uneven (-> movesDone %% 2 == 1)
  movesDone = sum(abs(board)) # abs(board) makes -1s to 1s, so we can just sum all fields to get the number of moves
  return(1 - 2 * (movesDone %% 2)) # subtract 2 from 1 only if movesDone is uneven
}
```



### 6
**Combine the output of the `getMove()` and the `whoseTurnIsIt()` functions to change your `board` by placing a 1 or -1 in the appropriate place.**
```{r eval=FALSE}
coordinates <- getMove()
# Check whose turn it is and then update "board"
board[coordinates[1], coordinates[2]] = whoseTurnIsIt(board)
```