Homework Week 3
========================================================

Name: | StudentNumber:
------|------
Max Hollmann | 2180812

Homework:
-----------

In the next two weeks, we're going to build a Tic-Tac-Toe game. The first step that's always important in programming is to think about the internal representations (what we've called "variables" upto now) that are necessary. In Tic-Tac-Toe the main representation is, of course, the game board. 

### 1

The game of tic-tac-toe is played on a board of 3x3, which might be represented in R by the following statement.
```{r}
gameboard <- matrix(0, nrow=3, ncol=3)
```

Moves can be represented by setting cells of this matrix to -1 (for player 1) or 1 (for player 2).
```{r}
gameboard[2,2] <- -1
gameboard
gameboard[1,2] <- 1
gameboard
```

Write a function (see template below) that returns -3 or 3 if there are three of the same markers in any row, and 0 otherwise. Use `rowSums()`.

```{r}
winnerSum <- function(sums) {
  if (any(sums == 3))  return(3)
  if (any(sums == -3)) return(-3)
  return(0)
}
winnerRow <- function(m) {
  s = rowSums(m)
  winnerSum(s)
}
```

### 2
Write a function that returns -3 or 3 if there are three of the same markers in any column, and 0 otherwise. Use `colSums()`.

```{r}
winnerCol <- function(m) {
  s = colSums(m)
  winnerSum(s)
}
```


### 3
Write a function that returns -3 or 3 if there are three of the same markers in either diagonal, and 0 otherwise. Use either `diag()`, or use direct indexing (e.g., statements like `gameboard[1,3]`).

```{r}
winnerDiag <- function(m) {
  s = c(
    sum(diag(m)),
    
    # rotate matrix by 90 degrees clockwise
    # code from http://stackoverflow.com/questions/16496210/rotate-a-matrix-in-r
    sum(diag(t(apply(m, 2, rev))))
  )
  winnerSum(s)
}
```

### 4
Write a function that checks to see if someone has won. Write a line of text on the screen (using `cat()`) to provide relevant output (e.g., “Player 1 wins!”).

```{r}
winner <- function(m) {
  w = c(winnerRow(m), winnerCol(m), winnerDiag(m))
  if (any(w == -3)) return(1)
  if (any(w == 3))  return(2)
  return(0)
}

m = matrix(c(
  -1, -1,  1,
   0,  1, -1,
   1, -1, -1
), nrow = 3)
print(m)
print("Player 1 is -1; player 2 is 1")
cat("Winner is player", winner(m), "\n")


m = matrix(c(
   1, -1, -1,
  -1,  1, -1,
   0, -1, -1
), nrow = 3)
print(m)
print("Player 1 is -1; player 2 is 1")
cat("Winner is player", winner(m), "\n")
```