In-class Challenge 2
========================================================

Name: | StudentNumber:
------|------
Max Hollmann | 2180812

Assignment:
-----------

### 1
Use R's built-in help to determine what the `rnorm()` function does. Describe it in one or two sentences.

It returns `n` random numbers from a normal distribution with the specified mean and standard deviation.


### 2
Choose a nice round integer between ten thousand and one million. Save it as a variable called `N` (we are going to use this as a sample size). Does this variable contain a scalar, vector, or matrix?

```{r}
N <- 1000
```

N is a scalar.

### 3

Draw N samples from a normal distribution, and save these samples in a variable called `samples`. (pick your own mean and standard deviation). Does samples contain a scalar, vector, or matrix?


```{r}
samples <- rnorm(N, 100, 30)
```

This returns a vector.

### 4

Suppose these numbers represent successive samples from some population, and you wanted to know the cumulative mean for your samples; that is, you want N values, each of which represents the mean of samples only up to that point. Example: if `x = c(1,2,6)`, then the cumulative mean vector would be `c(1,1.5,3)`. 

A first step to computing a mean is computing a sum. Use R's `help.search()` function to find the function to compute cumulative sums.

Save the cumulative sums in a new vector, called `sums`.

```{r}
sums <- cumsum(samples)
```

### 5

Each element of `sums` is a sum. Confirm that the last element of `sums` is the sum of all values in `samples`, using the `sum()` function. Use the `==` comparison to print the boolean value represing the (in)equality.

```{r}
tail(sums, 1) == sum(samples)
```

### 6

What do you have to do to use sums to compute cumulative means? Do it, and save the result to a variable called means.

```{r}
means <- sums / seq(1, length(sums))
plot(means)
```

### 7

Sample one random number from `1:10`, and write a set of `if-then` rules that prints to the console whether the sampled number if smaller than 3, smaller than 7, or larger or equal to 7.

```{r}
n <- sample(1:10, 1)
print(paste(n, "is ..."))
print(paste0(if(n >= 3) "not ", "smaller than 3"))
print(paste0(if(n >= 7) "not ", "smaller than 7"))
print(paste0(if(n < 7) "not ", "greater or equal to 7"))
```

### 8

Create a data frame that represents the grades of a group of 50 students in a course. The first column should contain a studentID drawn from the list of student IDs created by this command:

```{r}
studentID <- as.vector(outer(letters, letters, paste, sep = ""))
```

and the second column should represent the grade of the student.

```{r}
df <- data.frame(id = sample(studentID, 50), grade = sample(1:10, 50, replace = TRUE))
```

Now calculate the mean score of the students of this course and try to find a way to calculate what the proportion of students is that has passed this course. For this last assignment, study the next bit of code:

```{r}
mean(df$grade)
sum(df$grade >= 6)
```