In-class 5 Assignment
========================================================


The `createCanvas` and the 'drawHouse'-at-a-fixed-position function are given:

```{r}
createCanvas <- function(skyColor = "lightblue", earthColor="darkgreen") {
    plot(1,type="n",xlim=c(1,100),ylim=c(1,100),asp=1,
         ## Next arguments are to make sure no axes are plotted:
         xlab="",ylab="",axes=FALSE)
    rect(1,1,100,20,col=earthColor)
    rect(1,20,100,100,col = skyColor)
}

drawHouse <- function(brickColor="white",roofColor="red",doorColor="brown",windowColor="yellow") {
    ## Let's create a little house:
    rect(20,20,30,30,col=brickColor) # Base
    polygon(c(18,25,32),c(30,37,30),col=roofColor) # Roof
    rect(21,20,25,26,col=doorColor) # Door
    rect(26,23,29,26,col=windowColor,lwd=2) # Window
    lines(c(26,29),c(24.5,24.5),lwd=2)
    lines(c(27.5,27.5),c(23,26),lwd=2)
}
```

### 1 

Update the `createCanvas()` function so that one can also specify a sky color, and use a reasonable default.

### 2

First, update the `drawHouse` function so that a coordinate set can be provided:

```{r}
drawHouse <- function(x,y,brickColor="white",roofColor="red",doorColor="brown",windowColor="yellow") {
  rect(x, y, x + 10, y + 10, col=brickColor) # Base
  polygon(x + c(-2, 5, 12), y + c(10, 17, 10), col=roofColor) # Roof
  rect(x + 1, y, x + 5, y + 6, col=doorColor) # Door
  rect(x + 6, y + 3, x + 9, y + 6, col=windowColor, lwd=2) # Window
  lines(x + c(6, 9), y + c(4.5, 4.5), lwd=2)
  lines(x + c(7.5, 7.5), y + c(3, 6), lwd=2)
}
```

After you've written that function, you can recreate the plot with the more playful position of the houses:

```{r}
createCanvas()
for (x in seq(5,85,by=15)) {
    drawHouse(x+runif(1,0,3),sample(1:20,1))
}
```

### 3

Now, update the above code so that every house is a bit more individual, with, for example, a different colored front door. Run the function `colors()` to see which colors are available. One could, of course, `sample` the vector returned by `colors()` to select a color. 

However, if you feel more adventurous, you might also have a look at the last example shown on the help page for the function `colors()`. After executing that example, study the output of the example to get some inspiration on how to create a set "sort of similar" colors (hint: look for `nearRcolor`). 

```{r}
createCanvas()
for (x in seq(5,85,by=15)) {
  col = runif(3, 0, 1) # pick a random color for the bricks
  drawHouse(x+rnorm(1,0,3), sample(1:20,1),
    brickColor = do.call("rgb", as.list(col)),
    roofColor  = do.call("rgb", as.list(pmax(col - runif(3, 0, .4), 0))) # make the roof a bit darker, but a similar color
  )
}
```

### 4

Create a new function `cloud` that draws a cloud on the canvas. Use the `draw.circle` function, and make it as complex as you want...


```{r}
library(plotrix)
cloud = function(x, y) {
  size = round(runif(1, 6, 15))
  # alpha = .5
  alpha = NULL # no alpha; for compatibility
  for (i in 1:size) {
    draw.circle(
      x + rnorm(1, 0, size*.7), y + rnorm(1, 0, size*.2), # distribute circles over an area depending on size
      radius = rnorm(1, 5, 1),
      border = NA,
      col = do.call("rgb", as.list(c(
        pmin(    # make sure rgb values stay within 0:1
          pmax(
            c(.7, .7, .7) + rnorm(1, 0, .1),
            0
          ),
          1
        ),
        alpha
      )))
    )
  }
}


createCanvas()
for (x in seq(5,85,by=15)) {
  col = runif(3, 0, 1)
  drawHouse(x+rnorm(1,0,3), sample(1:20,1),
    brickColor = do.call("rgb", as.list(col)),
    roofColor  = do.call("rgb", as.list(pmax(col - runif(3, 0, .4), 0)))
  )
}
for (i in 1:3) {
  cloud(runif(1, 0, 100), runif(1, 30, 100))
}
```
